---
title: "Virginia Department of Environmental Quality Biological Monitoring Program
  Benthic Assessment Factsheet"
author: "Emma Jones"
date: "2/24/2021"
html_document:
  toc: true
  toc_float: true
always_allow_html: yes
params:
  assessmentDecision: 'NULL'
  SCI: 'NULL'
  habitat: 'NULL'
---

```{r setup, include=FALSE, message= FALSE}
knitr::opts_chunk$set(echo = FALSE)

assessmentDecision <- params$assessmentDecision
SCI <- params$SCI
habitat <- params$habitat
```


**Integrated Report Year:** &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; `r unique(assessmentDecision$IRYear)`

**River Basin:** &nbsp;&nbsp; `r unique(SCI$Basin)`

**Stream Name:** &nbsp;&nbsp;`r unique(assessmentDecision$StreamName)`

**Location Information:** &nbsp;&nbsp;`r unique(SCI$Sta_Desc)`

**Station ID:** &nbsp;&nbsp;`r unique(assessmentDecision$StationID)`

**Collection Method:** &nbsp;&nbsp;`r unique(SCI$Gradient)`

**Assessment Method: ** &nbsp;&nbsp;`r unique(assessmentDecision$AssessmentMethod)`

**Reviewer:** &nbsp;&nbsp; `r unique(assessmentDecision$Reviewer)`




assessment decision

```{r}
assessmentDecision 
```

SCI

```{r}
SCI
```

habitat

```{r}
habitat
```

