




### WQS Work

Now that all stations are at least organized for AU attribution, we need to do the same for WQS attribution. Like before, we will use whatever assessor QAed information we can get our hands on as a starting point to reduce the amount of spatial snapping required.

Starting with irData_join bc that has the sites that have WQS info already

```{r}

irData_missingWQS <- filter(irData_join, is.na(CLASS)) # these had no previous records

irData_finalWQS <- filter(irData_join, !is.na(CLASS))

# make sure we didn't lose anyone
nrow(irData_finalWQS) + nrow(irData_missingWQS) == nrow(irData_join)

```


Join sites missing WQS back previously populated station information.

```{r}
irData_missingWQS <- #filter(cit, FDT_STA_ID %in% irData_missing$FDT_STA_ID) %>%
   #bind_rows(filter(nonA, FDT_STA_ID %in% irData_missing$FDT_STA_ID)) %>%
  #bind_rows(filter(conventionals_D, FDT_STA_ID %in% irData_missing$FDT_STA_ID))
  left_join(dplyr::select(irData_missingWQS, UID:Longitude, BASIN_NAME, BASIN_CODE, SUBBASIN), 
            conventionals_D, by = c('FDT_STA_ID','Latitude', 'Longitude')) %>%
  dplyr::select(-geometry,geometry)
```


#### Polygon files

Since it is much faster to look for spatial joins by polygons compared to snapping to lines, we will run spatial joins by estuarine polys and reservoir layers first.

##### Estuarine Polygons

Find any sites that fall into an estuary WQS polygon.
  - see optional code to write those sites to a separate csv for future reference
3) Removes any estuarine sites from the data frame of unique conventionals sites that need WQS information.

```{r Filter Out Estuary Statewide, echo=F, results = 'hide'}}

estuaryPolys <- st_read('GIS/WQS_layers_04282020.gdb', layer = 'estuarinepolygons_04282020' , fid_column_name = "OBJECTID") %>%
  # Fix error in data
  mutate(Basin_Code = case_when(BASIN == '7' ~ 'Small Coastal', 
                                TRUE ~ as.character(Basin_Code)),
         BASIN = case_when(BASIN == '7' ~ '7A',
                           TRUE ~ as.character(BASIN))) %>%
   st_transform( st_crs(4326)) # transform to WQS84 for spatial intersection 


irData_missing_EstuaryPoly <- st_join(irData_missingWQS, estuaryPolys, join = st_intersects) %>%
      filter(!is.na(OBJECTID))

#write.csv(irData_missing_EstuaryPoly, 'irData_missing_EstuaryPoly.csv', row.names = F) 
# you can change the file location like so:
#write.csv(irData_missing_Estuary, 'C:/Assessment/2020/dataProcessing/irData_missing_Estuary.csv', row.names = F) 

irData_missingWQS_noEP <- filter(irData_missingWQS, ! FDT_STA_ID %in% irData_missing_EstuaryPoly$FDT_STA_ID)
rm(estuaryPolys) # remove from memory
```

Below is the table of sites that are estuarine.

```{r estuarySitesTable, echo=F}
DT::datatable(irData_WQS_EstuaryPoly %>% st_drop_geometry(), escape=F, rownames = F, options = list(scrollX = TRUE))
#View(irData_WQS_EstuaryPoly)
```

```{r,echo=F}
cat(paste('Removing the above sites, the unique sites have gone from ', nrow(irData_missingWQS),' to ',nrow(irData_missingWQS_noEP),'. The next step is to find the lake/reservoir stations and link them to the appropriate AU and WQS for analyses in the Lake Assessment App.', sep=''))
```


##### Reservoir Polygons

```{r inlineText3, echo=F}
cat(paste('Working with the ', nrow(irData_missingWQS_noEP),' sites that did not connect to a STATION_ID/FDT_STA_ID from last cycle, we will first do a spatial join to the reservoir/lakes WQS to see if any sites are lake sites before using the more computationally intensive stream snapping process.', sep=''))
```


```{r reservoirStatewideWQS, echo=F, results = 'hide'}

reservoirWQS <- st_read('GIS/WQS_layers_04282020.gdb', layer = 'lakes_reservoirs_04282020' , fid_column_name = "OBJECTID") %>%
  st_transform(4326)

#irData_missingWQSsubB_Lakes <- st_join(reservoirWQS, irData_missingWQS_noEP, join = st_intersects) %>%
#    filter(!is.na(FDT_STA_ID)) %>% # only keep rows where join successful
#    mutate(`Point Unique Identifier` = FDT_STA_ID, 
#           `Buffer Distance` = 'Within Polygon') %>%
#    dplyr::select(`Point Unique Identifier`, `Buffer Distance`, OBJECTID:Shape)
  


## holder for stations to drop from further analyses
stationsToRemove <- data.frame(FDT_STA_ID = NA, OBJECTID_Assigned = NA)

## Go through sites in each basin
for(i in 1:length(unique(irData_missingWQS_noEP$BASIN_CODE))){
  # find lake WQSs, if Any
  irData_missing_Lakes <- st_join(filter(reservoirWQS, BASIN == unique(irData_missingWQS_noEP$BASIN_CODE)[i]),
                                  irData_missingWQS_noEP, join = st_intersects) %>%
    filter(!is.na(FDT_STA_ID)) %>% # only keep rows where join successful
    mutate(`Point Unique Identifier` = FDT_STA_ID, 
           `Buffer Distance` = 'Within Polygon') %>%
    dplyr::select(`Point Unique Identifier`, `Buffer Distance`, OBJECTID:Shape)
  
  # Organize all lake sites from previous assessment info
  lakeStations <- filter(irData_final, grepl('L_', ID305B_1) | grepl('L_', ID305B_2) | grepl('L_', ID305B_3) |
                           STATION_TYPE_1 == "L" | STATION_TYPE_2 == "L" | STATION_TYPE_3 == "L") %>%
    filter(BASIN_CODE == unique(irData_missingWQS_noEP$BASIN_CODE)[i]) %>%
    rbind(filter(irData_join, FDT_STA_ID %in% irData_missing_Lakes$`Point Unique Identifier`))

  # save lake sites to special result for assessor to review, match riverine output
  # this is going to differ slightly from the riverine output in that tbl_output isn't necessary since all sites that don't fall into a lake (or estuary) AU will be
  # processed as riverine AND input_sites will contain stations that fell into lake AU and previously attributed lake sites
  lake_snapList_AU <- list('sf_output' = irData_missing_Lakes,
                           'inputSites' = lakeStations)
  
  stationFixes <- data.frame(FDT_STA_ID = as.character(irData_missing_Lakes$`Point Unique Identifier`), 
                             ID305B_Assigned = as.character(irData_missing_Lakes$ID305B))
  stationsToRemove <- bind_rows(stationsToRemove, stationFixes)
  
  saveRDS(lake_snapList_AU,paste0("data/preAnalyzedRegionalAUdata/", assessmentRegion,
                                  "/Lacustrine/", unique(reservoirAUs$Basin)[i], ".RDS"))

}


# and remove lake AU sites from the sites without AUs

irData_missing_NoAU <- mutate(irData_missing, ID305B_1 = NA) %>% # need column for snapping tools
  filter(!(FDT_STA_ID %in% stationsToRemove$FDT_STA_ID))

# update irData_join so fixed lake sites won't try to snap to riverine AUs
irData_join_fixed <- right_join(irData_join, stationsToRemove %>% drop_na(), by = 'FDT_STA_ID') %>%
  mutate(ID305B_1 = ID305B_Assigned,
         STATION_TYPE_1 = 'L') %>% 
  dplyr::select(-ID305B_Assigned) 
  

irData_join <- filter(irData_join, !FDT_STA_ID %in% irData_join_fixed$FDT_STA_ID) %>%
  rbind(irData_join_fixed)

rm(reservoirAUs) # remove from memory
```


